Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-27 paper.tex
minor fixes
Explain swapping memory results

\subsection{Swapping Memory Overhead}

@@

\subsubsection{Memory (TODO: SPAI)}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_rss}
    \caption{RSS while touching pages while swapping for random benchmark.}
\end{figure}

>>>>

\subsection{Swapping Memory Overhead}
\label{swapping_memory_overhead}

@@

\subsubsection{Memory}
Figure \ref{fig:swap_rss} shows the Resident Set Size of the system for the
experiments described in section \ref{swapping_memory_overhead}. The
\texttt{cont} workloads write to  adjacent 4KB pages in the address space. A
huge page of size 2MB is allocated (TODO: Is it 2MB?) when a new page is touched
initially. Subsequent 4KB pages that are touched are subpages of the 2MB page
allocated initially. As a result, the memory used by the workload is almost
equal to the amount of memory it has written to. The RSS thus increases linearly
until the system begins to swap when the number of free pages falls below a
threshold. The \texttt{rand} workload on the other hand writes to pages that are
not adjacent, and likely not subpages of a single huge page. As a result, a huge
page is allocated with almost every write, and the system starts to exhaust its
memory and begins swapping very quickly. Memory made available by kswapd is
quickly consumed by further writes and hence the memory used by the workload
continues to stay close to its peak value. As expected, the behavior is the same
irrespective of the size of the swap file.

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_rss}
    \caption{RSS while touching pages while swapping for random benchmark.}
    \label{swap_rss}
\end{figure}
